---
title: "p8105_hw1_hj2660"
author: "Hyun Jin Jung"
date: "2023-09-18"
output: html_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(moderndive)
library(ggplot2)
```

### Problem 1

Install the **moderndive** package and load **early_january_weather** dataset.

```{r}
data("early_january_weather")
```



```{r, echo=FALSE, results='hide'}
colnames(early_january_weather)
```

The names of variables in early_january_weather: *origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour*

```{r, echo=FALSE, results='hide'}
nrow(early_january_weather)
```

```{r, echo=FALSE, results='hide'}
ncol(early_january_weather)
```

The dataset early_january_weather includes **358 rows** and **15 columns**. 

```{r, echo=FALSE}
temp <- early_january_weather$temp 
```


```{r, echo=FALSE, results='hide'}
mean(temp)
```

The mean temperature is **39.58212**.
```{r, echo=FALSE, results='hide'}
sd(temp)
```

#### Scatterplot of Temperature vs Time_Hour

```{r, echo=FALSE, results='hide',message=FALSE}
ggplot(data = early_january_weather, aes (x = time_hour, y = temp, color = humid)) + geom_point() 
ggsave("temp vs time_hour by humid.png")
```
The scatterplot shows how temperature increases as time_hour increases, with gradient colors representing humidity levels. Patterns in the scatterplot shows positive correlations between temperature, time_hour, and humidity.

### Problem 2

Create a data frame

```{r, echo=FALSE, results='hide'}
my_df <- data.frame(
  random_numeric = rnorm(10), # Random sample of size 10 from a Normal distribution
  logical_vector = rnorm(10) > 0, # Logical vector indicating if elements are greater than 0
  character_vector = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"), # Character vector
  factor_vector = factor(sample(1:3, 10, replace = TRUE), levels = c(1, 2, 3))  # Factor vector with 3 levels
)
```

##### Calculate the mean of each variable
```{r, echo=FALSE, results='hide', warning=FALSE}
mean(pull(select(my_df, random_numeric)))
mean(pull(select(my_df, logical_vector)))
mean(pull(select(my_df, character_vector)))
mean(pull(select(my_df, factor_vector)))
```
Mean of **random_numeric** is 0.13001. <br>
Mean of **logical_vector** is 0.5. <br>
Mean of **character_vector** and **factor_vector** does not work because these are not numeric or logical.



